% Copyright 2004 by Till Tantau <tantau@users.sourceforge.net>.
%
% In principle, this file can be redistributed and/or modified under
% the terms of the GNU Public License, version 2.
%
% However, this file is supposed to be a template to be modified
% for your own needs. For this reason, if you use this file as a
% template and not specifically distribute it as part of a another
% package/program, I grant the extra permission to freely copy and
% modify this file as you see fit and even to delete this copyright
% notice. 

\documentclass{beamer}
\usepackage{graphicx}
\graphicspath{ {images/} }

% There are many different themes available for Beamer. A comprehensive
% list with examples is given here:
% http://deic.uab.es/~iblanes/beamer_gallery/index_by_theme.html
% You can uncomment the themes below if you would like to use a different
% one:
%\usetheme{AnnArbor}
%\usetheme{Antibes}
%\usetheme{Bergen}
%\usetheme{Berkeley}
%\usetheme{Berlin}
%\usetheme{Boadilla}
%\usetheme{boxes}
%\usetheme{CambridgeUS}
%\usetheme{Copenhagen}
%\usetheme{Darmstadt}
\usetheme{default}
%\usetheme{Frankfurt}
%\usetheme{Goettingen}
%\usetheme{Hannover}
%\usetheme{Ilmenau}
%\usetheme{JuanLesPins}
%\usetheme{Luebeck}
%\usetheme{Madrid}
%\usetheme{Malmoe}
%\usetheme{Marburg}
%\usetheme{Montpellier}
%\usetheme{PaloAlto}
%\usetheme{Pittsburgh}
%\usetheme{Rochester}
%\usetheme{Singapore}
%\usetheme{Szeged}
%\usetheme{Warsaw}

\title{Wagabond destination finding app}


\author{Dali Szilard, Szanto Zoltan, Gergely Patka}

\date{HackTGM, 2017}

% Delete this, if you do not want the table of contents to pop up at
% the beginning of each subsection:
\AtBeginSubsection[]
{
  \begin{frame}<beamer>{}
    \tableofcontents[currentsection,currentsubsection]
  \end{frame}
}

% Let's get started
\begin{document}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}{}
  \tableofcontents
  % You might wish to add the option [pausesections]
\end{frame}

% Section and subsections will appear in the presentation overview
% and table of contents.

%%% bevezeto: mi a problema-> milyen megoldasunk van ra
\section{Introduction}

\subsection{Where to go to have fun?}

\begin{frame}{Where to go to have fun?}{You could always explore some more.}

  \begin{itemize}
  \item {Where to go for a drink?    
  }
  \item {Where to go for a nice meal?   
  }
  \item {New place or your old town, you could always explore some more.
   
  }
  \end{itemize}
\end{frame}

\subsection{Our solution}

\begin{frame}{Wagabond the city exploring app}{Our solution for your problem}
  \begin{itemize}
  \item {Multiplatform app for ease of use
  }
  \item {Explore pubs, coffe shops, restaurants, museums, etc.
  }
  \end{itemize}
\end{frame}

%%% technikai megoldas... nagyvonalakban az app-rol; mi tortenik a hatterben (fuzzy.ai, php, backend stb)
\section{What is under the hood?}

\subsection{Construction of the system}

\begin{frame}{Construction of the system}
  \begin{itemize}
  \item {MVC    
  }
  \item {Active Record     
  }
  \item {Composer package management system   
  }
  \item {Android client   
  }

  \end{itemize}
\end{frame}

\subsection{Used technologies}

\begin{frame}{Used technologies}{The construction blocks of the app}
  \begin{itemize}
  \item {fuzzy.ai: a fuzzy logic API that can learn using user feedback
  }
  \item {Google maps API: to locate the places, and you   
  }
  \item{Google Fused Location API: to know where you are
  }
  \end{itemize}
\end{frame}

\begin{frame}{Fuzzy logic powered by fuzzy.ai}{The rules to find a suitable location}
  \begin{itemize}
  \item {distance (0.99): How far are you from the place 
  }
  \item {sponsor (0.2): Our partners can get a slightly better score
  }
  \item {rating value (0.3): How expensive is the place
  }
  \item {rating location (0.4): How nice is the place
  }
  \item {rating service (0.4): How good is the service
  }
  \item {rating cleanliness (0.3): How clean is it?
  }
  \end{itemize}
\end{frame}

%%% ez mar a vege... 
\section{Further development potential}

\section{Demo}

\subsection{Wagabond App demo}

\begin{frame}{Wagabond App demo}
\end{frame}

\subsection{Further features}

\begin{frame}{Further features}{Further features that we want to include}
  \begin{itemize}
  \item {More options for places    
  }
  \item {Web interface   
  }
  \item {User feedback for the locations   
  }
  \item {Machine learning to improve results   
  }
  \end{itemize}
\end{frame}

\subsection{Monetization potential}

\begin{frame}{}
  \begin{itemize}
  \item {Partnership with pubs, restaurants, etc.    
  }
  \item {New section in the App for upcoming event (payed by advertisers)   
  }
  \end{itemize}
\end{frame}


% summarize the shit
\section*{Summary}

\begin{frame}{Summary}
  \begin{itemize}
  \item
    City exploring app
  \item
    Potential for monetization
  \item
    Continuous integration "like" with github webhooks, Composer and database migration
  \end{itemize}
\end{frame}

\begin{frame}{Thank you for the attention}
\end{frame}

\end{document}


